---
title: "Zipcode and CPD Analysis"
author: "Martin Gleason, MS"
date: "1/27/2020"
output: html_document
---

## Summary of ask:
The following questions are guiding this GIS analysis:

* Which Chicago Police Department Districts and Cook County zipcodes intersect? 
* How many zipcodes are in each particular CPD district? 
* How does this zipcode interaction impact case assignment by zipcode?

## Method
The first step was to create a map of Cook County zipcodes, and overlay this feature with the [CPD district shapefile.](https://data.cityofchicago.org/Public-Safety/CPD-districts/7hhi-ktqw) This file is part of the [Chicago Data Portal](https://data.cityofchicago.org) and can be used with a variety of GIS products. Zipcode integration was a bit more difficult.

The first issue is technical -- [Zipcodes are not polygons, but linear features.](http://www.georeference.org/doc/zip_codes_are_not_areas.htm) Zipcodes represent postal routes, and may include neighborhoods, buildings, or even US Navy ships. While zipcodes are frequently used in stastical models and maps, these zipcodes are frequently derrived from [Zipcode Tabulation Areas.](https://www.census.gov/programs-surveys/geography/guidance/geo-areas/zctas.html)

### Leaflet Map of Cook County Zipcodes and Chicago Police Districts

```{r setup, include=FALSE, error = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
library("tidyverse")
library("here")
library(kableExtra)

source(here("scripts/load_shapes.R"))

```

```{r map, include=TRUE, warning = FALSE, message = FALSE, echo = FALSE}
cc_cpd_zip
```

## 
