---
title: "Zip code and CPD Analysis"
author: "Martin Gleason, MS"
date: "1/31/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    css: ["../libs/css/report.css", "../libs/css/report-fonts.css"]
---

## Summary of ask:
The following questions are guiding this GIS analysis:

* Which Chicago Police Department Districts and Cook County zip codes intersect? 
* How many zip codes are in each particular CPD district? 
* How does this zip code interaction impact case assignment by zip code?

## Method
The first step was to create a map of Cook County zip codes, complete with a boundary of the entire county, and then overlay it with the [CPD district shapefile.](https://data.cityofchicago.org/Public-Safety/CPD-districts/7hhi-ktqw) Setting up the district boundaries was easy, as this file is part of the [Chicago Data Portal](https://data.cityofchicago.org) and can be used with a variety of GIS products. Zip code integration was a bit more difficult.

The first issue seems to be a distinction without a difference: [Zipcodes are not polygons, but linear features.](http://www.georeference.org/doc/zip_codes_are_not_areas.htm) Zip codes represent postal routes, and may include neighborhoods, a single building, or a United States Naval vessel . While zip codes are frequently used in statistical models and maps, these zip codes are frequently derived from [Zipcode Tabulation Areas,](https://www.census.gov/programs-surveys/geography/guidance/geo-areas/zctas.html) which are maintained not by the USPS, but by the US Census Bureau. ZCATS are not 1:1 representation of Zip codes, and may vary as much as 20% with regard to areas covered. For cook county, this distinction may impact up to 3 zip codes, which in turn could impact the assignment of dozens, if not hundreds, of cases.

The second issue was more technical: How to get the zip code shape files. Pitney/Bowes sells a GIS solution for $399/year. Their product does not depend on the user knowing GIS data, and is regularly updated. The US Census Bureau offers TIGER/Line files as part of their open data project. TIGER/Line files are large, and require additional filtering to get to specific geographic locales. Cook County GIS does have a ZCTAS based layer in ArcGIS; however, at present my access to running analysis is limited. To generate this report, I pulled the ZCTAS file from the US Census Bureau and used the ```sf``` package to create and analyze geographic data. 

The interactive map below is the sum of this work. Hovering over a Zip code creates a pop up message of the zip code, where as markers are CPD district names and headquarters. Lastly, CPD districts are also mapped to a specific color.


### Leaflet Map of Cook County Zip codes and Chicago Police Districts

```{r setup, include=FALSE, error = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
library("tidyverse")
library("here")
library(kableExtra)
source(here("scripts/load_shapes.R"))
source(here("scripts/polygon_comparison.R"))



```

```{r map, include=TRUE, warning = FALSE, message = FALSE, echo = FALSE}
cc_cpd_zip
```

### Intersection Table
This table calculates the number of zip codes that intersect with a district. This means if a line of a zip codes intersects with the border of a CPD district -- including overlapping borders -- it is counted as an intersection. A tabular view provides additional insight into the difficulty of assignment by zip code: Any zip code solution will require a Zip code and district dividing line. A family whose home is "on the line" between a zip codes and districts will needs additional logic to solve. 

```{r intersection_table, include=TRUE, echo = FALSE, warning = FALSE, message = FALSE}
intersection_tibble %>%
  kable(format = "html", 
        caption = "Count of Intersections Between City of Chicago Police Districts and Zip codes",
        col.names = c("CPD District Number",
                      "Number of Zipcode Intersections")) %>%
  kable_styling(bootstrap_options = c("responsive", "bordered", "striped"),
                full_width = TRUE)

```
### Intersection Plot
This visualization breakdown the number of intersections of zip codes in a particular district. 
```{r intersection_plot, include=TRUE, fig.caption = "Count of Zipcode Intersections within CPD Districts",  echo = FALSE, warning = FALSE, message = FALSE}

intersection_plot
```

How this dividing line is maintained in future versions of our instance of Supervisor also needs to be considered: Zip codes and districts will change. Moving the district, zip code, or dividing line becomes more cumbersome and complicated because it is set manual by the developers. A full [GIS Point in Polygon ](http://wiki.gis.com/wiki/index.php/Point_in_polygon) solution, either by MS SQL Server, ArcGIS or Google Maps API provides a more modular solution that will be easier to maintain and alter during the lifetime of the cFive contract.